Document Expansion with External Collections for Information Retrieval

### 2016-09-05 paper.tex
some work on introduction (needs more work!!)

Relevance modeling is an extremely influential pseudo-relevance feedback technique that helps to allievate the problem of vocabulary mismatch. Instead of assuming that queries are observations sampled from \textit{document} models, we assume that both queries and documents are observations sampled from a \textit{relevance} model (RM) \cite{Lavrenko2001}. We can use this idea to expand the query representation into an estimate of the relevance model as explained in Section \ref{section.expanding.model.rm} and rank documents by the similarity of their estimated language model to the estimated RM.

As a form of pseudo-relevance feedback, part of the relevance modeling process involves assuming that top-ranked documents are relevant to the query. Although this assumption is generally untrue, it is true of enough top-ranked documents that the estimated RM will be of good quality. That is, initially retrieved documents provide a good estimate of the underlying relevance model \textit{in their aggregate}; taken individually, documents are not assumed to accurately represent the underlying RM.

We suggest that, given that a top-ranked document is, like a query, considered a limited observation of terms from a relevance model, documents may be expanded to better reflect their underlying relevance model. In this paper, we propose a method of document expansion that closely mirrors the process of relevance modeling. This document expansion process serves many of the same roles as traditional relevance modeling without excluding the use of RMs; indeed, our document expansion process is complementary to query expansion.

\textbf{Talk about external collections and combining evidence.}

>>>>

Relevance modeling is an extremely influential pseudo-relevance feedback technique that helps to allievate the problem of vocabulary mismatch. Instead of assuming that queries are observations sampled from \textit{document} models, we assume that both queries and documents are observations sampled from a \textit{relevance} model (RM) \cite{Lavrenko2001}. We can use this idea to expand the query representation into an estimate of the relevance model (see Section \ref{section.expanding.model.rm} for more details) and rank documents by the similarity of their estimated language model to the estimated RM.

As a form of pseudo-relevance feedback, part of the relevance modeling process involves assuming that top-ranked documents are relevant to the query. Although this assumption is not uniformly true, it is true of enough top-ranked documents that the estimated RM will be of good quality. That is, initially retrieved documents provide a good estimate of the underlying relevance model \textit{in their aggregate}; taken individually, documents are not assumed to accurately represent the underlying RM.

% We suggest that, given that a top-ranked document is, like a query, considered a limited observation of terms from a relevance model, documents may be expanded to better reflect their underlying relevance model. In this paper, we propose a method of document expansion that closely mirrors the process of relevance modeling. This document expansion process serves many of the same roles as traditional relevance modeling without excluding the use of RMs; indeed, our document expansion process is complementary to query expansion.

Relevance modeling makes use of a query likelihood weight, $P(Q|D)$, which helps to quantify the degree to which each document should contribute to the final RM. However, given that individual documents are not considered accurate representations of the relevance model $R$, we may reasonably be concerned that our estimate of $P(Q|D)$ is the result of chance. This concern applies to both high and low estimates of $P(Q|D)$, and, if true, we would expect this problem to affect the quality of our relevance models. We suggest that this may be solved by expanding documents: adding terms to a document should improve our estimates of the underlying language model and in turn improve the quality of retrieval results and relevance models based on these expanded documents.

In this paper, we propose a method of document expansion that closely mirrors the process of relevance modeling. This document expansion process serves many of the same roles as traditional relevance modeling without excluding the use of RMs; indeed, our document expansion process is complementary to query expansion. However, the concerns that lead us to expand documents in the first place---potentially inaccurate term probability estimates drawn from top-ranked documents---also apply to our document expansion procedure.

To help alleviate this, we introduce a general method of incorporating external document collections into the document expansion process. Our idea is that, while documents in individual collections may suffer from fairly high term frequency variance and other forms of bias, documents from multiple collections will likely average out to create good general purpose estimates. Specifically, we use Wikipedia as our external collection. We believe that, as a general encyclopedia, Wikipedia is most likely to provide unbiased language model estimates; that is, estimates of $P(Q|D)$ calculated where $D$ is from Wikipedia seem likely to exhibit minimal variance.
